---
title: "An Rmarkdown Example"
author: "Thomas J. Leeper"
date: 2018-01-30
output: pdf_document
---

```{r data, echo=FALSE, results="hide"}
library("knitr")
opts_chunk$set(echo=FALSE)
library("gapminder")
library("ggplot2")
suppressPackageStartupMessages(library("stargazer"))
```

There are some descriptive statistics about the data:

```{r table1}
knitr::kable(aggregate(cbind(lifeExp, pop, gdpPercap) ~ year, data = gapminder, FUN = mean))
```

Figures 1 shows some general patterns.

```{r figure1}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, colour = continent)) + 
  geom_point()
```
  
And the main regression are shown in the table.

```{r table2, results = "asis"}
stargazer::stargazer(
  x1 <- lm(lifeExp ~ I(pop/1000000) + gdpPercap, data = gapminder),
  x2 <- lm(lifeExp ~ I(pop/1000000) + gdpPercap + year + factor(continent), data = gapminder),
  header = FALSE
)
```

```{r inlinenumbers, results="hide"}
pop_effect1 <- sprintf("%0.2f", coef(x1)[2L])
pop_effect2 <- sprintf("%0.2f", coef(x2)[2L])
```

To summarize, here are some main results. To summarize, here are some main results. 
The estimated effect of population size on life expectancy is `r pop_effect1`.
Using continent and year controls, however, changes this effect to: `r pop_effect2`.
